Automating Verification of MPC Security

### 2023-06-09 popl24/bruteforce.tex
checkpoint

\section{Brute Force Verification}

@@

$$
g\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) =\begin{array}[t]{l}
\elet{\stores'}{\solve{(\mems(\vars\ \be))}{\be}}{}\\
  \{\extend{\store}{\view{\cid}{w}}{\etrue} \mid \store \in \stores' \} \cup
  \{\extend{\store}{\view{\cid}{w}}{\efalse} \mid \store \in \stores - \stores' \}\end{array}
$$

@@

@@

>>>>

\section{Brute Force Verification}
\label{section-bruteforce}

@@

$$
g\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) =\begin{array}[t]{l}
\elet{\stores'}{\solve{\stores}{\be}}{}\\
  \{\extend{\store}{\view{\cid}{w}}{\etrue} \mid \store \in \stores' \} \cup
  \{\extend{\store}{\view{\cid}{w}}{\efalse} \mid \store \in \stores - \stores' \}\end{array}
$$

@@

\begin{lemma}
  For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}) = \{ \store \in \store \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$
  for some $\cid$.
\end{lemma}

\begin{lemma}
  For all $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$:
  $$
  (\mathit{foldl}\ g\ \mems(S \cup F)\ \prog) =
  \{ \store \in \mems(S\cup F \cup V) \mid \config{\store_{S \cup F}}{\prog} \redxs \config{\store}{\varnothing} \}
  $$
\end{lemma}

@@

\begin{mathpar}
  \logit{x \mapsto 1} = x

  \logit{x \mapsto 0} = \neg x

  \logit{\{ x_1 \mapsto \beta_1, \ldots, x_n \mapsto \beta_n\}} =
  \logit{x_1 \mapsto \beta_1} \wedge \cdots \wedge \logit{x_n \mapsto \beta_n}

  \mathit{clauses}(x,\{ \store_1,...,\store_n \}) = x \gets \logit{\store_1} \vee \cdots \vee x \gets \logit{\store_n}
\end{mathpar}

$$
\mathit{map}\ \mathit{clauses}\ (\mathit{map}\ f\ \prog)
$$
